\section{Publications}

\subsection{Journal Publications}

\cvitem{}{C. ~Soraghan, C. ~Markham, \underline{F. ~Matthews},  \&  T. ~Ward,
  {\bfseries Triple wavelength LED driver for optical brain--computer interfaces.} \emph{
  Electronics Letters\/}, vol.~45, no.~8, pp. 392--394. 2009.}

\cvitem{}{ \underline{F. ~Matthews}, B.~Pearlmutter, T.~Ward, C.~Soraghan, and C.~Markham,
  {\bfseries Hemodynamics for brain-computer interfaces,} \emph{Signal Processing
  Magazine, IEEE}, vol.~25, no.~1, pp. 87--94, 2008.}

\cvitem{}{  T.~E. Ward, C.~J. Soraghan, \underline{F. ~Matthews}, and C.~M. Markham, {\bfseries A concept for
  extending the applicability of constraint induced movement therapy through
  motor cortex activity feedback using a neural prosthesis,}
  \emph{Computational Intelligence and Neuroscience}, 2007.}
  
\subsection{Conference Publications}
\cvitem{}{ \underline{F. ~Matthews}, C.~Soraghan, T.~E. Ward, C.~Markham and B.~A. Pearlmutter
   {\bfseries Software platform for rapid prototyping of NIRS brain-computer interfacing techniques}
   \emph{30th Annual International Conference Of The IEEE Engineering In Medicine And Biology Society}, Vancouver,
   Canada, 2008.}

\cvitem{}{ C.~Soraghan, \underline{F. ~Matthews}, C.~Markham, B.~A. Pearlmutter, R.~O'Neill, T.~E. Ward
   {\bfseries A 12-Channel, real-time near-infrared spectroscopy instrument for brain-computer interface applications}
   \emph{30th Annual International Conference Of The IEEE Engineering In Medicine And Biology Society}, Vancouver,
   Canada, 2008.}

\cvitem{}{ C.~J. Soraghan, T.~E. Ward, \underline{F. ~Matthews}, C.~Markham
    {\bfseries Optical Safety Assessment of a Near-Infrared Brain-Computer Interface}
   \emph{16th IET Irish Signals and Systems Conference} Galway, Ireland, 2008.}

\cvitem{}{ C. ~Soraghan, \underline{F. ~Matthews}, C. `Markham, B. ~A. Pearlmutter, and T. ~E. Ward
   {\bfseries Biophotonic Methods for Brain-Computer Interfaces}  (2007)
   \emph{Photonics Ireland}, Galway, Ireland}

\cvitem{}{ C.~Soraghan, \underline{F. ~Matthews}, D.~Kelly, T.~Ward, C.~Markham, B.~Pearlmutter, and
  R.~O'Neill, {\bfseries A dual-channel optical brain-computer interface in a gaming
  environment,} in \emph{Proceedings of the 9th International Conference on
  Computer Games: AI, Animation, Mobile, Educational and Serious Games}, Dublin
  Institute of Technology, Ireland, Nov. 2006.}

\cvitem{}{ J. ~Foody, \underline{F. ~Matthews}, D. ~Kumar, C. ~Markham, T. ~Ward and B. ~Caulfield,
   {\bfseries A USB Interfaced Motion Capture Sensor, Using Tri-Axis Magnetic/Inertial Sensors For Use In Kinematic Studies}
   \emph{3rd European Medical and Biological Engineering Conference EMBEC'05 and IFMBE European Conference on Biomedical
   Engineering}, Prague, Czech Republic, 2005}