\section{Industry Experience}
\cventry{June,2021 -- Present}{Principal Architect}{Medable Inc.}{Palo Alto}{}{
\begin{itemize}
\item Create {\&} lead a network of architects
\item Provide application architectural solutions to meet business requirements.
\item Lead team members to develop architectural strategies and guidelines.
\item Work in compliance with company policies and procedures for operational efficiency.
\item Recommend new technologies to management to develop robust applications.
\item Analyze and troubleshoot architecture-related issues in a timely fashion.
\end{itemize}}
\cventry{Nov,2017 -- June,2021}{Senior Developer, Backend}{Medable Inc.}{Palo Alto}{}{
\begin{itemize}
\item Provide architectural support to product development
\item Design and develop advanced applications for the various platforms (e.g. Android, iOS, backend, and web front-end)
\item Unit-test code for robustness, including edge cases, usability, and general reliability
\item Perform Bug fixing and improving application performance
\item Collaborate with cross-functional teams to define, design, and ship new features
\item Continuously discover, evaluate, and implement new technologies to maximize development efficiency
\end{itemize}}
\cventry{Feb,2013 -- Nov,2017}{Head Of Software Engineering}{Galvanic}{Dublin}{}{
Responsible design, implementation, management and delivery to market of HIPAA compliant stress management devices, infrastructure and cross-platform apps targeting the health care, corporate and consumer markets. \newline{}%
Tasks \& Responsibilities:%
\begin{itemize}
\item Management of the software team and development life cycle of the PIP apps and the My Pip cloud infrastructure
\item Publishing of multiple apps to both iOS and Android App Stores
\item Development and maintenance of a native iOS, Android and OSX SDKs for the PIP
\item Developing plug-ins from the SDK to cross-platform development environments (Marmalade \& Unity)
\item Development of native and cross-platform apps for use with the PIP
\item Development and Delivery of a HIPAA compliant consumer cloud service including server and client (Web and native app) components. 
\item Development and Delivery of a HIPAA compliant, subscription based corporate and health care cloud service to allow our customers gain insights into the well being of patients and employees. 
\end{itemize}}

\Mycventry{Dec,2011 -- Feb,2013}{Software Developer}{5th Province Ventures, Dublin}{}{}{Developer for the iOS and Android app for WISP, a location based social-networking system.\newline{} 
Tasks \& Responsibilities:%
\begin{itemize}
\item Feature Design and Implementation
\item Managing source control systems
\item Integration of new features with the custom XMPP server back-end
\item In app development done using C++ and javascript with tools developed with python
\end{itemize}}

\cventry{May,2009 -- Dec,2011}{Software Team Leader for Irish Robocup team. Post-Doctoral Fellow}{Hamilton Institute, NUI Maynooth}{Maynooth, Co. Kildare}{}{Tasks \& Responsibilities:
\begin{itemize}
  \item Developing software systems for the RoboEireann Standard Platform League (SPL) team
  \item Coordination maintenance of the overall software project
  \item Supervisory roles for students on work placement or 10 week internship projects (Summer Internship in Autonomous Robotics (SIAR))
  \item Administrative duties include organizing and coordinating travel for the team to compete in International competitions
\end{itemize}}